\bf An HMM-based part-of-speech tagger for Turkish

### 2015-11-16 proposal/proposal.tex
Update proposal

\title{\bf An HMM-based part-of-speech tagger for Turkish}
\author{Your Name}
\date{Due date: 16 November 2015 at 11:59 PM Central time}

@@

% Briefly survey the most salient prior work that relates to the problem you wish
% to solve. This section should cite relevant sources. This section should be at
% least one to two paragraphs in length.
The most important advancement in the computational linguistics of Turkish is
the NLP framework ``Zemberek'' by \citet{akin2007zemberek}. Although it started
out as an NLP tool for the Turkish language, Zemberek moved on to become a
framework for dealing with all Turkic languages

@@

\citet{Weaver_memo_1949} proposed that machine translation \ldots
%
The square root of 4 is 2 \citep{1952_06_17_BarHillel}.

>>>>

\title{\bf An HMM-based part-of-speech tagger for Turkish}
\author{Ayberk Tosun\\\texttt{tosun2@illinois.edu}}
\date{}

@@

% Briefly survey the most salient prior work that relates to the problem you wish
% to solve. This section should cite relevant sources. This section should be at
% least one to two paragraphs in length.
The most important advancement in the computational linguistics of Turkish is
the NLP framework ``Zemberek'' by \citet{akin2007zemberek}. Although it started
out as an NLP tool for the Turkish language, Zemberek moved on to become a
a tool for processing all Turkic languages. Zemberek has been immensely useful
for linguistic research on Turkish. Yet, it is undeniable that once-popular
Java does not provide an ideal environment for writing NLP software.

The widely cited \citet{oflazer1994tagging} outlines the implementation of a
tool for both morpheme glossing and POS tagging, that has ``98-99 \%'' accuracy. This
tool is based on a morphological specification of Turkish and makes use of a
morphological processor called ``PC-Kimmo'' \citep{antworth1991pc}.

@@
